\begin{thebibliography}{99}
\addcontentsline{toc}{chapter}{Bibliografía}
\bibitem{jade99}
  F. Bellifemine, A. Poggi, G. Rimassa,
  \emph{JADE - A FIPA-compliant agent framework}.
  CSELT internal technical report,
  1999.
\bibitem{dev01}
  F. Bellifemine, A. Poggi, G. Rimassa,
  \emph{Developing multi-agent systems with a FIPA-compliant agent framework}.
  Software - Practice And Experience,
  2001.
\bibitem{coord00}
  R. S. Cost, Y. Labrou, T. Finin,
  \emph{Coordinating Agents using Agent Communication Languages Conversations}.
  2000. 	
\bibitem{apl03}
  Dastani et al.,
  \emph{A Programming Language for Cognitive Agents: Goal Directed 3APL}.
  Proceedings of the First Workshop on Programming Multiagent Systems: Languages, frameworks, techniques, and tools,
  2003.
\bibitem{coop96}
  Doran et al.,
  \emph{On Cooperation in Multi-Agent Systems. The Knowledge Engineering Review}.
  1996.
\bibitem{delp04}
  A. J. García, G. R. Simari,
  \emph{Defeasible logic programming: An argumentative approach}.
  Journal of Theory and Practice of Logic Programming,
  2004.
\bibitem{int05}
  A. J. García, M. Tucat, G. R. Simari,
  \emph{Interaction Primitives for Implementing Multi-agent Systems}.
  Interaction Primitives for Implementing Multi-agent Systems,
  2005.
\bibitem{mult99}
  M. Huhns, L. Stephens,
  \emph{Multiagent Systems and Societies of Agents}.
  Multiagent Systems: A Modern Approach to Distributed Artificial Intelligence,
  1999.
\bibitem{arg98}
  N. R. Jennings et al.,
  \emph{Argumentation-Based Negotiation}.
  Proceedings of the International Workshop on Multi-Agent Systems,
  1998.
\bibitem{soc99}
  S. Kalenka, N. R. Jennings,
  \emph{Socially Responsible Decision Making by Autonomous Agents}.
  Proceedings of the 5th International Colloquium on Cognitive Science,
  1999.
\bibitem{neg96}
  J. Müller,
  \emph{Negotiation Principles}.
  Foundations of Distributed Artificial Intelligence,
  1996.
\bibitem{mod91}
  A. Rao, M. Georgeff,
  \emph{Modeling rational agents within a BDI-architecture}.
  Proceedings of the Second International Conference on Principles of Knowledge Representation and Reasoning,
  1991.
\bibitem{bdi95}
  A. S. Rao, M. P. Georgeff,
  \emph{BDI Agents: From Theory to Practice}.
  Proceedings of the First International Conference on Multi-Agent Systems,
  1995.
\bibitem{arg02}
  S. V. Rueda, A. J. García, G. R. Simari,
  \emph{Argument-based Negotiation among BDI Agents}.
  Journal of Computer Science and Technology,
  2002.
\bibitem{ia99}
  M. Wooldridge,
  \emph{Intelligent Agents}.
  Multiagent Systems, The MIT Press,
  1999.
\bibitem{brat99}
    M. E. Bratman,
    \emph{Intention, Plans, and Practical Reason}.
    Cambridge University Press,
    1999.
\bibitem{searle1985}
	J.R. Searle,
  \emph{Intentionality, an Essay in the Philosophy of Mind}.
  Cambridge University Press,
  1983.

\end{thebibliography}