\begin{thebibliography}{9}

\bibitem{gray08}
  Shon Harris et al.,
  \emph{Gray Hat Hacking: The Ethical Hacker's handbook}.
  McGraw Hill,
  2da Edici\'on,
  2008.
\bibitem{art03}
  Jon Erickson,
  \emph{Hacking: The art of exploitation}.
  1era Edici\'on,
  2003.
\bibitem{spray10}
  Yu Ding et al.,
  \emph{Heap Taichi: Exploiting Memory Allocation Granularity in Heap-Spraying Attacks}.
  Annual Computer Security Applications Conference (ACSAC),
  2010.
\bibitem{mud03}
  Frank Ch. Eigler,
  \emph{Mudflap: Pointer Use Checking for C/C++}.
  GCC Developers' Summit,
  2003.
\bibitem{gim03}
  Jason Merrill,
  \emph{GENERIC and GIMPLE: A New Tree Representation for Entire Functions}.
  GCC Developers' Summit,
  2003.
\bibitem{ssa03}
  Diego Novillo,
  \emph{Tree SSA: A New Optimization Infrastructure for GCC}.
  GCC Developers' Summit,
  2003.
\bibitem{sta03}
  Perry Wagle,
  \emph{StackGuard: Simple Stack Smash Protection for GCC}.
  GCC Developers' Summit,
  2003.
\bibitem{spray210}
  Piotr Bania,
  \emph{JIT spraying and mitigations}.
  Kryptos Logic Research,
  2010.
\bibitem{ret07}
  Hovav Shacham,
  \emph{The Geometry of Innocent Flesh on the Bone: Return-into-libc without Function Calls (on the x86)}.
  Proceedings of ACM CCS,
  2010.
\bibitem{rop10}
  Piotr Bania,
  \emph{Security Mitigations for Return-Oriented Programming Attacks}.
  Kryptos Logic Research,
  2010.
\bibitem{shell07}
  Chris Anley et al.,
  \emph{The Shellcoder's Handbook: Discovering and Exploiting Security Holes}.
  Willey Publishing Inc.,
	2da Edici\'on,
  2010.
\bibitem{sec06}
  James C. Foster et al.,
  \emph{Writing Security Tools and Exploits}.
  Syngress,
	1era Edici\'on,
  2006.
\bibitem{ssp00}
  Hiroaki Etoh et al.,
  \emph{Protecting from stack-smashing attacks}.
  IBM Research,
  2000.
\bibitem{ker05}
  Diego Bovet et al.,
  \emph{Understanding the Linux Kernel}.
  O'Reilly,
	3era Edici\'on,
  2005.
\bibitem{owl11}
  \emph{OpenWall Project}.
  http://www.openwall.com/.
\bibitem{dlm11}
  \emph{Doug Lea's malloc implementation}.
  http://g.oswego.edu/dl/html/malloc.html.
\bibitem{pax11}
  \emph{Pax Documentation: Design}.
  http://pax.grsecurity.net/docs/pax.txt.
\bibitem{pax112}
  \emph{Pax Documentation: ASLR}.
  http://pax.grsecurity.net/docs/aslr.txt.
  
\end{thebibliography}